Estimating Real-Time Highstreet Footfall from Wi-Fi Probe Requests

### 2018-12-07 review/response.md

## First review comments
--------------------------------------------------------------------------------

@@

Title : Estimating Real-Time Highstreet Footfall from Wi-Fi Probe Requests

Manuscript id : IJGIS-2018-0340

Comments dated : 28-Oct-2018

## 1 Editor
--------------------------------------------------------------------------------

@@

9. When submitting your revised manuscript, you will be able to respond to
the comments made by the reviewers in the space provided. You can use this
space to document any changes you make to the original manuscript. In order
to expedite the processing of the revised manuscript, please be as specific
as possible in your response to the reviewers.

10. Please delete any redundant files before completing the submission.

> Thank you for the detailed instructions. All of these have been taken in
> consideration and checked for creating the revised manuscript for the final
> submission.

## 2 Reviewer-1
--------------------------------------------------------------------------------

@@

### 2.2 General Comments

1. The idea of clustering frames using sequence number has been introduced in
[1]. This work needs to be cited when introducing the proposed clustering
algorithm.

   [1] Mathy Vanhoef, Célestin Matte, Mathieu Cunche, Leonardo Cardoso, Frank
Piessens. Why MAC Address Randomization is not Enough: An Analysis of Wi-Fi
Network Discovery Mechanisms. ACM AsiaCCS, May 2016, Xi’an, China. 2016,

> Thank you. We have included a citation to the source, as well as one other
> recent addition to this fast-developing literature.

@@

2. The author considered that the hashing of MAC address is a good way to
protect users privacy, as some MAC address collected by the device may not be
random. However hashing of MAC address cannot be considered as a proper
anonymization technique (see [2] and
http://webpolicy.org/2014/03/19/questionable-crypto-in-retail-analytics/); at
best it can be considered as an obfuscation. [2] Levent Demir, Mathieu
Cunche, Cédric Lauradoux. Analysing the privacy policies of Wi-Fi trackers.
Workshop on Physical Analytics, Jun 2014, Bretton Woods, United States. ACM,
2014

> Thank you for pointing this out. In the revised version of the paper we
> have made reference to this discussion, while also making clear the
> anonymisation is ensured by the system architecture that processes and
> curates the data.  Specifically we rotated the random salt used to hash the
> MAC addresses regularly to prevent any kind of tracking of the users across
> a longer period of time with which the hashing process is carried out.

@@

> Thank you very much for these very positive comments. The paper reports on
> extensive methodological research and field implementation and is, we
> believe, cutting edge in its finding. It also has important implications
> for our understanding of the functioning of smart cities, and these
> implications are discussed in greater detail in the revised version.

2. "Wi-Fi beacon technologies to access the Internet". In Wi-Fi, beacons are
management frames used by Access Point for service discovery. They do not
provide Internet access. "Wi-Fi Access Point to access ..."

> Thank you. We have corrected and clarified the point.

3. "Wi-Fi antennae regularly broadcast a special type of signal" -> the
antenna is just the part ensuring that the signal is correctly emitted, but
it is not the source. In this context it is better to use a more general
concept and refer to the "Wi-Fi network interface" (or Wi-Fi interface) as
the element broadcasting a signal.

@@

9. Could you provide more information on the application used for counting
(Clicker)

> This simple application was developed specifically for the project for
> Android platform. More details on the application has been included in the
> revised manuscript.

10. "Though the recycling of sequence number r after 4000 leads to multiple
classifications reported on single device, the magnitude of error is greatly
reduced." This sentence is not clear. And the cycle length is not 4000 but
4096 = 2^12.

> Thank you. This point has been noted and accommodated into the revised
> version.

@@

11. Regarding the issue of cycling sequence number, one could use a distance
with a modulo : di,j = di - dj mod 4096.

> Thank you very much for the suggestion. We carried out some tests on a
> sample data of 1910 probe requests comprising of google phones with
> randomised MAC addresses captured in the pilot study and found that only
> around 0.5% of the probe requests encountered the recycling of sequence
> number. Which, in our opinion, doesn't influence the results in any
> significant way considering the context. We have also included this in our
> revised manuscript.

@@

1. Challanges

2. "These are deemed to be consumer data because devices carried by consumers
routinely probe for a consumer service, specifically a Wi-Fi connection.
Monitoring the probes from such devices provides an indication" This sentence
is not clear.

3. "Though Wi-Fi F is a ‘location-less’ technology, ", please clarify what
you mean by that.

4. "privacy infringement" may not be the best word as infringement relate to a
law or a regulation. Privacy breach or leak may be a better choice.

@@

5. Wireshark and not WireShark.

6. "We hypothesize that an adjustment factor could be arrived at for each
location of data collection, ""This calibration can be carried over
periodically and the frequency to improve the quality of the estimation."
something wrong in both sentences.

> Thank you for picking up these minor lapses. All have been corrected or
> clarified in the revised version of the paper.

## 3 Reviewer-2
--------------------------------------------------------------------------------

@@

2. P6 l27, please provide more information regarding how you defined the
threshold for low/high signal strength when eliminating the background noise.
This was also unclear in the case study on P8, where the authors repeatedly
mixed up classification and clustering. Neither k-means nor hierarchical
clustering is considered a “classification algorithm” as claimed in p8 l26.
Very few details were provided regarding the parameter setting of these
analyses.

> Thank you. The reference to clustering has been amended. The specifics of
> the thresholds used have been included, and the techniques justified in
> more detail.

3. P6 l30-31, in the phone shop example, the authors mentioned that it is
possible to identify background noise based on a sharp rise of the request
number; however, this will also eliminate the regular pedestrian flow in that
shop and cause additional inaccuracy. Please clarify.

> Thank you. Clarified in the revised version. It is know with preliminary
> investigation that the received signal strength indicator decreases with
> increasing distance between the mobile device and the base station. This
> change is also found to be exponential as opposed to linear. With this
> context When we install a sensor to have a clear view of the pedestrian
> footpath in front of it, we make sure that all the devices beyond a certain
> distance will report similarly low signal strength. This threshold is
> identified using the k-means algorithm to find the natural break in the data.
> We have found that this successfully isolates a farther stationary source
> of large number of probe requests such as a phone shop or a restaurant next
> door, Bus stops etc.  This doesn't work when the source of error is within
> the range of the footfall. As shown in our examples 2,4. Here our
> methodology fails to provide sufficient accuracy.

@@

4. P7 l21, how often does the recycling of sequence number occur, and how
will this impact the reliability of your analysis? Please provide more
details.

> The recycling of the sequence number occurs every 4096 counts. From our
> experiments we observed that a device staying next to device actively
> searching recycles the sequence number 1-2 times in a 30 mins interval. On
> average this is expected to be much less than this. When the device doesn't
> probe as frequently. We have included more details regarding the cycling of
> sequence numbers and have mentioned method to overcome this as mentioned
> by other reviewer. The change in implementing the method is estimated to be
> --% which we found to be not significant in our context.

@@

> This is a valid concern. Which we tried to clarify in the revised
> manuscript.  Our motivation is not to attempt to track the movements of
> individuals, although we do attempt to accommodate measurement variations
> attributable to micro-site location of the sensors. In related work, we
> have carried out controlled comparison of sensor measures obtained from
> adjacent store locations, and examined correspondence with retail unit
> function. This enables identification of the differences in dwell time
> between, for example, fast food outlets and clothes shops. This full
> analysis requires addition of store till data and the analysis is detailed.
> For this reason we include only a short reference to this extension of our
> analysis here. We also aim this method to count footfall accurately at
> locations rather than the flow of footfall between those locations. But as
> demonstrated in we can infer the relation or flow between the locations
> using other probabilistic approaches.
>
> Lee J, Nemati S, Silva I, Edwards BA, Butler JP, Malhotra A. Transfer
> entropy estimation and directional coupling change detection in biomedical
> time series. Biomed Eng Online. 2012;11:19. Published 2012 Apr 13.
> doi:10.1186/1475-925X-11-19
>
> Vicente R, Wibral M, Lindner M, Pipa G. Transfer entropy--a model-free
> measure of effective connectivity for the neurociences. J Comput Neurosci.
> 2010;30(1):45-67.

7. P10 l48, how was the adjustment factor determined?

> The adjustment factor is calculated as the ratio between the manual counts
> to the counts calculated from sensor for the sample period. This is used to
> adjust future counts at the same locations. We have included the
> clarification on the revised manuscript.

## 4 Reviewer-3
--------------------------------------------------------------------------------

@@

### 4.2 General Comments

Some areas where I would like to see more detail:

1. It would have been interesting to understand the temporal characteristics
for a week pedestrian footfall. How to consider this situation in your study?
Why do you choose time range from 12:30 to 13:00 hrs ?

> Thank you. Our related work (cited below) examines daily, weekly and
> seasonal variation, and wil be the subject of future papers.
>
> Lugomer, K., & Longley, P. (2018). Towards a Comprehensive Temporal
> Classification of Footfall Patterns in the Cities of Great Britain (Short
> Paper). In LIPIcs-Leibniz International Proceedings in Informatics (Vol.
> 114).  Schloss Dagstuhl-Leibniz-Zentrum fuer Informatik.
>
> There was no reason for selecting the time in the pilot study. The location
> was chosen for it it known to have high number of randomised probe requests
> and has one of the highest footfall in London. For the main study the
> counting was done such that each location has at least 2/3 counts in the
> same time interval.

@@

3. Methodology: Will you draw a diagram of the Methodology?

> We have resequenced some of the material in response to Referee 2 and,
> cognisant of over-all length requirements, think that this (rather than a
> diagram) addresses your concerns.

4. Performance Analysis: How about the performance for collecting data using
PostgreSQL? Did you compare Apache Flink and Spark Streaming for real-time
data collecting?

> This is an interesting point in the context of big data and tools for
> tackling big data. Though the data set here is large enough to make desktop
> computing unfeasible, it is neither big nor fast enough for a large scale
> big data system. An open source and free toolkit comprising of text
> processing tools and relational database management system was enough to
> handle the complexity, size and speed of the data. The toolkit employed here
> involves PostgreSQL, Bash, Unix tools for text processing (sed, awk, sort,
> join), Node.js and R. The same toolkit proved to be useful in the larger
> project (smart street sensor) providing near real-time delivery of data.

### 2019-01-21 review/review_02/response.md

## Reviewer 1
--------------------------------------------------------------------------------

I appreciate the authors’ effort to address my comments in the revised draft.
The manuscript has been greatly improved. I have a few minor comments:

 1. p9 l36-40: When determining the threshold for high/low signal strength, did
    you just set the number of clusters equals to 2 for kmeans and hierarchical
    clustering? If so, you should explicitly say so in the explanation.

> Thanks for the feedback. We have included this explicitly in the revised
> manuscript.

 2. Please enlarge and recreate the sub-figures in Figure 3. This figure is
    difficult to read in its current format.

> We agree. A more legible version of Figure 3 has been included in the revised
> manuscript.

 3. I would suggest adding the following paper to the literature review:
    Torrens, P. M. (2008) Wi-Fi Geographies. Annals of the Association of
    American Geographers, 98(1), 59-84.

> Thanks for pointing out this important literature that we missed to cite.  We
> have included this reference in the literature review.

## Reviewer 2
--------------------------------------------------------------------------------

The revised version of this paper is of better quality and the authors have
taken into account reviewers' comments.

 1. However, Figure 3 needs a slight improvement. In the final version, all the
    figures must be of good quality, with similar formatting (size).

> We agree. A more legible version of Figure 3 has been included in the revised
> manuscript.

 2. Please check the format of the references.

> Thanks for pointing this out. We have checked and fixed the format of the
> references

More specific comments can be found in the following,

 3. Page 8, Could you give more description about your real-time experimental
    data? (Like data size, the total number of records)

> Thank you for the feedback. Similar to the Oxford street case study, we have
> included more descriptive statistics on the data collected under the case
> study in Section 5 - Table 2.

 4. Page 10, “we observed that the best thresholds for time and sequence
    numbers in the clustering algorithm is around 16 and 60 respectively”,
    Could you give more detail information?

> Thank you for the feedback. These thresholds are arrived at through a trial
> and error. We have further clarified the process along with a more legible
> illustration which is shown in Figure 3.

 5. Page 14. “There are obvious extensions to understanding the ebbs and flows
    of activities in the 24-hour smart city.” Could you give some suggestions
    to use your method in these extensions?

> Thanks for the input. We have included few examples and cited recent
> research demonstrating them.

### 2019-01-21 paper/sections/main_study.tex
almost done

\begin{table}
	\tbl{Locations where sensors were installed}
	{\begin{tabular}{clll} 
		\toprule
		 ID & Location & Type & Installation notes\\
		 \midrule
		 1 & Camden High Street & Phone Shop & Bus stop in front\\
		 2 & Central St.Giles Piazza & Restaurant & Seating area on both sides\\
		 3 & Holborn Underground Station & Information Kiosk & Overlooks station entrance\\
		 4 & Brunswick Center & Fast Food Restaurant & Has seating area on one side\\
		 5 & The Strand & Tea Shop & Has phone shop next door \\
		 \bottomrule
	\end{tabular}}
	\label{locations-table}
\end{table}

@@

The results of the first stage of the filtering process along with the
thresholds are shown in Table \ref{errors_table}.  Confirming our intuition, we
see that the location 2 has the most MAPE followed by location 4 while rest of
them have highly reduced MAPE.  It is significant that this method alone
reduces our margin of error by a 50 - 100\% from the raw counts without any
cleaning.  This makes the signal strength filtering quick and ideal method for
practical applications which doesn't require absolute numbers such as creating
large aggregated indexes to show long term trends.  We also see that the
success of the signal strength filtering can be improved significantly by
installing sensors such that the pedestrians and noise are at different
distances from the sensor and are the field of measurement is distinct from the
surroundings however noisy it might be.

We then run the sequence numbers based clustering process on the rest of the
probe requests to reduce the MAPE by almost 50 - 100\% on all the sensors except
for location 3.  Location 3 is an outlier among all the other sensors since it
is the only one with large amount of pedestrians very close to the sensor.  This
may be causing the over filtering caused by the previous process.  We finally
run the calibration process where we calculate the adjustment factors from the
ratio between the manual counts to the counts calculated for the sample period
as shown in Table \ref{errors_table}.  We the use them to adjust the counts to
achieve a MAPE ranging from 10 - 50\%. We can see that the sensors with people
moving right next to them tend to under-count with our methodology while sensors
with seating next to them tend to over-count significantly. However, using the
filtering process, we can reduce the error to almost 10\% closer to that of the
ground truth.

>>>>

\begin{table}
    \tbl{Locations where sensors were installes, volume and speed of probe requests collected by
    the sendor and total pedestrians manually counted. The data occupies around 1.8 GB on disk 
    when encoded in text format.}
	{\begin{tabular}{clllccc} 
		\toprule
         ID & Location & Type & Installation notes & Probe Requests & Footfall\\
         & & & & x10\textsuperscript{6} (per min) & No. (per min)\\
		 \midrule
         1 & Camden High Street & Phone Shop & Bus stop in front & 9.9 (297) & 3683 (33)\\
         2 & Central St.Giles & Restaurant & Seating area on both sides & 3.9 (169) & 0346 (05)\\
         3 & Holborn Station & Info. Kiosk & Overlooks station entrance & 4.3 (303) & 2956 (46)\\
         4 & Brunswick Center & Fast Food & Has seating area on one side & 3.4 (210) & 0960 (12)\\
         5 & The Strand & Tea Shop & Has phone shop next door & 8.4 (382) & 1969 (21)\\
		 \bottomrule
	\end{tabular}}
	\label{locations-table}
\end{table}

@@

The results of the first stage of the filtering process along with the
thresholds are shown in Table \ref{errors_table}.  Confirming our intuition, we
see that the location 2 has the most MAPE followed by location 4, while the rest
of them have highly reduced MAPE.  It is significant that this method alone
reduces our margin of error by 50 - 100\% from the raw counts without any
cleaning.  This makes the signal strength filtering a quick and ideal method for
practical applications, one which doesn't require absolute numbers such as
creating large aggregated indexes to show long-term trends.  We also found that
the success of the signal strength filtering can be improved significantly by
installing sensors so that the pedestrians and source of noise are at different
distances from the sensor. This ensures that the distribution of signal
strengths within the field of measurement is distinct from that of the
surroundings.

We then ran the sequence numbers based clustering process on the rest of the
probe requests to reduce the MAPE by almost 50 - 100\% on all the sensors except
for location 3.  Location 3 is an outlier among all the other sensors since it
is the only one with large amount of pedestrians very close to the sensor.  This
may be the reason behind the over filtering observed in the previous process.
We finally ran the calibration process where we calculated the adjustment
factors from the ratio between the manual counts to the sensor based counts for
the sample period as shown in Table \ref{errors_table}.  We used them to adjust
the counts to achieve a MAPE ranging from 10 - 50\%. We observed that the
sensors with people moving right next to them tend to under-count with our
methodology, while sensors with seating next to them tend to over-count
significantly. However, using the filtering process, we can reduce the error to
almost 10\% closer to that of the ground truth.

### 2019-01-21 paper/sections/pilot_study.tex
almost done

begin{table}
\tbl{Comparison of clustering algorithms with a sample of 40000 probe requests}
{\begin{tabular}{lcc} 
	\toprule
	 Algorithm					& Time (s) 	& MAPE (\%) \\
	\midrule
	 Quantile					& 0.002 	&  27 \% \\
	 K-Means			 		& 0.007 	& -23 \% \\
	 Hierarchical Clustering	& 172.520 	&  -9 \% \\
	 Bagged Clustering 			& 0.135 	& -30 \% \\
	 Fisher 					& 3.034 	& -30 \% \\
	 Jenks Natural Break 		& 556.279 	& -30 \% \\
	 \bottomrule
\end{tabular}}
\label{classification-table}
\end{table}

@@

We then classified the probe requests as `high signal strength' and `low signal
strength' using various one dimensional clustering algorithms such as k-means,
quantile, hierarchical clustering, bagged clustering, fisher and jenks natural
breaks. The results are shown in Table \ref{classification-table}. We found that
while hierarchical clustering and jenks gave us fairly low errors, they were too
resource intensive for practical use with a larger dataset. We also found that
k-means gave the quickest results with the lowest MAPE, closely followed by
quantile algorithm. The cut-off point or threshold for the collected data with
which we could classify as high and low was -71 dBm. We then removed all the
probe requests which reported `low signal strength' and repeated the same
aggregation process as before to produce footfall count. This process resulted
in a footfall count with a net MAPE of 30\%. Although the results are
encouraging we are still not completely confident that our filtering process is
removing noise or has any correlation the configuration of sensor or position of
the mobile devices. These concerns need to be addressed with a larger survey
with multiple locations of varying orientations.

\begin{figure}
   \begin{center}
        \vspace{10pt}
        \includegraphics [width=\linewidth,trim=10 30 10 75,clip]
            {images/pilot_clustering_params.png}
        \caption{The clustering process was repeated with both increasing sequence
            number threshold ($\alpha$) and time threshold ($\beta$), until we
            arrived at the lowest parameters where the know device (black line) is
            clustered as a single device.}
        \label{pilot_clustering_params}
    \end{center}
\end{figure}

\begin{figure}
\centering
\subfigure[Clustering probe requests based on increasing sequence numbers 
	present in them.]
	{\resizebox*{0.45\linewidth}{!}
	{\includegraphics{images/pilot_clustering.jpeg}}}
\hspace{20pt}
\subfigure[Comparison of sensor based counts with the ground truth.]
	{\resizebox*{0.45\linewidth}{!}
	{\includegraphics{images/pilot_comparison.jpeg}}}
\caption{The results of the pilot study demonstrating the validity of the
	methodology.} 
\label{pilot_results}
\end{figure}

The next challenge was to identify the probe requests which are generated by the
same device irrespective of the MAC randomisation process. We used the algorithm
defined in Section \ref{methodology} and assigned a unique identifier or
signature to each probe request, independent of their the MAC addresses. Since
we didn't know the nature or frequency of the MAC address randomisation process,
we used the surveyor's mobile device as a reference. As the surveyor's device
was being actively used to count pedestrians and it's Wi-Fi module was kept
active without establishing connection to any network, the device was known to
be continuously probing for new networks. We also knew that the OUI of the
device was 'Google' and the device was regularly randomising it's MAC address,
thus providing us an excellent reference with which we could optimise the
parameters for our clustering algorithm. Using this reference device we observed
that the threshold for time $\alpha$ and the threshold for sequence numbers,
$\beta$ are 16 seconds and 60 respectively via trial and error. This process is
shown in Figure \ref{pilot_clustering_params}. This was undertaken on top the
filtering done based on signal strength, and only for the probe requests with
randomised MAC addresses. Figure \ref{pilot_results} shows the results of this
clustering process on a small set of randomised probe requests. The probe
requests with different randomised MAC address are shown by the coloured points
and the lines joining them show that those probe requests were most likely be
generated by the same device. We finally aggregated the probe requests as we did
before but with the device signature rather than MAC addresses. This results in
a footfall count with a MAPE of -18\% compared to the manual count. A comparison
of minute by minute counts resulting from different filtering processes along
with the ground truth is shown in Figure \ref{pilot_results} illustrating the
promising effectiveness of the methods.

>>>>

\begin{table}
\tbl{Comparison of clustering algorithms with a sample of 40000 probe requests}
{\begin{tabular}{lcc} 
	\toprule
	 Algorithm					& Time (s) 	& MAPE (\%) \\
	\midrule
	 Quantile					& 0.002 	&  27 \% \\
	 K-Means			 		& 0.007 	& -23 \% \\
	 Hierarchical Clustering	& 172.520 	&  -9 \% \\
	 Bagged Clustering 			& 0.135 	& -30 \% \\
	 Fisher 					& 3.034 	& -30 \% \\
	 Jenks Natural Break 		& 556.279 	& -30 \% \\
	 \bottomrule
\end{tabular}}
\label{classification-table}
\end{table}

@@

We then classified the probe requests as `high signal strength' and `low signal
strength' using various one dimensional clustering algorithms such as k-means,
quantile, hierarchical clustering, bagged clustering, fisher and jenks natural
breaks with the number of clusters set as 2. The results are shown in Table
\ref{classification-table}. We found that while hierarchical clustering and
jenks gave us fairly low errors, they were too resource intensive for practical
use with a larger dataset. We also found that k-means gave the quickest results
with the lowest MAPE, closely followed by quantile algorithm. The cut-off point
or threshold for the collected data with which we could classify as high and
low was -71 dBm. We then removed all the probe requests which reported `low
signal strength' and repeated the same aggregation process as before to produce
footfall count. This process resulted in a footfall count with a net MAPE of
30\%. Although the results are encouraging we are still not completely
confident that our filtering process is removing noise or has any correlation
the configuration of sensor or position of the mobile devices. These concerns
need to be addressed with a larger survey with multiple locations of varying
orientations.

\begin{figure}
\begin{center}
\vspace{10pt}
\includegraphics [width=0.85\linewidth,trim=10 15 10 15,clip]
    {images/pilot_clustering_params_rev.png}
\caption{The clustering process was repeated with both increasing sequence
    number threshold ($\alpha$) and time threshold ($\beta$), until we arrived
    at the lowest parameters where the know device (black line) is clustered as
    a single device.}
\label{pilot_clustering_params}
\end{center}
\end{figure}

\begin{figure}
\centering
\subfigure[Clustering probe requests based on increasing sequence numbers 
	present in them.]
	{\resizebox*{0.45\linewidth}{!}
	{\includegraphics{images/pilot_clustering_rev1.jpeg}}}
\hspace{20pt}
\subfigure[Comparison of sensor based counts with the ground truth.]
	{\resizebox*{0.45\linewidth}{!}
	{\includegraphics{images/pilot_comparison.jpeg}}}
\caption{The results of the pilot study demonstrating the validity of the
	methodology.} 
\label{pilot_results}
\end{figure}

The next challenge was to identify the probe requests which are generated by
the same device irrespective of the MAC randomisation process. We used the
algorithm defined in Section \ref{methodology} and assigned a unique identifier
or signature to each probe request, independent of their the MAC addresses.
Since we didn't know the nature or frequency of the MAC address randomisation
process, we used the surveyor's mobile device as a reference. As the surveyor's
device was being actively used to count pedestrians and it's Wi-Fi module was
kept active without establishing connection to any network, the device was
known to be continuously probing for new networks. We also knew that the OUI of
the device was 'Google' and the device was regularly randomising it's MAC
address, thus providing us an excellent reference with which we could optimise
the parameters for our clustering algorithm. We then, by increasing the
thresholds in steps of 1, found the minimum possible threshold for time and
sequence numbers at which the algorithm clusters the reference device properly
without over clustering the other probe requests.  This process is shown in
Figure \ref{pilot_clustering_params}. We observed that the threshold for time
$\alpha$ and the threshold for sequence numbers, $\beta$ are 16 seconds and 60
respectively This was undertaken on top the filtering done based on signal
strength, and only for the probe requests with randomised MAC addresses. Figure
\ref{pilot_results} shows the results of this clustering process on a small set
of randomised probe requests. The probe requests with different randomised MAC
address are shown by the coloured points and the lines joining them show that
those probe requests were most likely be generated by the same device. We
finally aggregated the probe requests as we did before but with the device
signature rather than MAC addresses. This results in a footfall count with a
MAPE of -18\% compared to the manual count. A comparison of minute by minute
counts resulting from different filtering processes along with the ground truth
is shown in Figure \ref{pilot_results} illustrating the promising effectiveness
of the methods.
